\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
%\moderncvtheme[blue]{casual}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
\moderncvtheme[green]{classic}                % idem
\usepackage{textcomp}
%\usepackage{times}
% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using
\usepackage[pdfstartview=FitH]{hyperref}%[pdfstartview=FitH]
%生成带超链接的目录，CJKbookmarks=true使我成功%一般位于导言区最后.pdfstartview=FitH可以使得生成的pdf打开时显示适当宽度
% adjust the page margins
\usepackage[scale=0.8]{geometry}
\recomputelengths                             % required when changes are made to page layout lengths
\hypersetup{pdfpagemode=None}  %不显示书签

\setlength\footskip{0pt}
\addtolength\textheight{6em}


% personal data
\firstname{Daijiang}
\familyname{Li}
\title{Curriculum Vitae}               % optional, remove the line if not wanted
\address{State Key Laboratory of Biocontrol,}{School of Life Sciences, Sun Yat-Sen University,\\ Guangzhou, Guangdong Province, China}    % optional, remove the line if not wanted
\mobile{+86~15913105622}                    % optional, remove the line if not wanted
%\phone{86-10-39332984}                      % optional, remove the line if not wanted
%\fax{86-10-39332983}                          % optional, remove the line if not wanted
\email{daijianglee@gmail.com}                      % optional, remove the line if not wanted
%\extrainfo{additional information (optional)} % optional, remove the line if not wanted
%\photo[64pt]{ldj1}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted
\quote{\small{"Go for the messes -- that's where the action is." -- Steven Weinberg\\
OBJECTIVE: Ph.D degree in EEB}}  %               % optional, remove the line if not wanted

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page



\begin{document}
\maketitle
\vspace*{-40pt}
\section{\textsc{Education}}
\cventry{2008-Present}{Master of Science (MSc.) in Restoration Ecology}{School of Life Sciences, Sun Yat-Sen University (SYSU)}{GRE scores (Jun 2010): Verbal 610 (88\%), Quantitative 800 (94\%), Analytical 3.0 (10\%)}{ibt-TOEFL scores (Sep 2010): 106/120}{}
\cventry{2004-2008}{Bachelor of Science (BSc.) in Ecology}{School of Life Sciences, Yunnan University (YNU)}{Over all GPA: 84.4/100, Major GPA (Ecology-related courses)87/100}{}{}{}

\section{\textsc{Honors}}
\cventry{2010}{Education Scholarship for Graduate Student (Fellowship)}{}{SYSU}{China}{}
\cventry{2009}{Education Scholarship for Graduate Student (Fellowship)}{}{SYSU}{China}{}
\cventry{2009}{Excellent prize of presentation in English}{}{SYSU}{China}{}
\cventry{2008}{Second Award of National Scholarship}{}{YNU}{China}{}
\cventry{2007}{Second Award of Donglu Scholarship}{}{YNU}{China}{}
\cventry{2006}{Second Award of Donglu Scholarship}{}{YNU}{China}{}

\section{\textsc{Experience}}
\subsection{\textsc{Research}}
\cventry{Jun.2009-Present}{Independent research}{I am using the litter-bag method to characterize leaf litter decomposition rates on soil surface with varying degrees of evenness, in the context of increasing dominance of climbing plants in tropical forests}{
\newline $\bullet$ Explore relationships between leaf litter evenness and decomposition rates
\newline $\bullet$ Understand consequences of increasing dominance of climbing plants in tropical forests for regional carbon cycling}{}{}
\cventry{Jan.2010-Sep.2010}{Coauthor of a National Natural Science Foundation of China (NSFC) grant proposal}{The role of plant functional group identity and diversity in resisting exotic plant species invasion}{No.31030015,  \textyen 1,900,000}{
\newline $\bullet$ Learned how to write grant proposals
\newline $\bullet$ Learned how to apply grants}{}
\cventry{Jul.2009-present}{Core member in a Natural Science Foundation of Guangdong Province}{The mechanisms of native invasion in the context of global change}{
\newline $\bullet$ Enlarged the definition of biological invasion
\newline $\bullet$ Explored differences of resource utilization efficiency between non-native and native invaders}{}{}
\cventry{Mar.2009-present}{Group member in a Guangdong Province Forest Science Project}{Restoration of forests which have been
damaged by the snow storm of 2008}{
\newline $\bullet$ Chose the position of experimental plots
\newline $\bullet$ Conducted vegetation survey in experimental plots
\newline $\bullet$ Accelerated restoration of damaged forest ecosystem by several measures}{}{}
\cventry{Apr.2009-Jun.2009}{Group member in a NSFC project}{The restoration of degraded watershed ecosystem of the Pearl River}{
\newline $\bullet$ Applied ecological theories to practice of restoration}{}{}
\cvline{Apr.2009}{\textbf{Group member in translating and publishing the Chinese version of the book} \emph{Brian Walker and David Salt, Resilience Thinking: Sustaining Ecosystems and People in a Changing World. Island Press, USA. ISBN: 9781597260930}}
\cventry{Dec.2008}{Group member in a Danxia Mountain Project funded by China's application for the world natural heritage}{Identify characteristics of the Danxia Mountain's ecosystem and biological diversity}{
\newline $\bullet$ Identified and recorded organisms in experimental plots
%\newline $\bullet$ recorded temperature and humidity in experimental plots
%\newline $\bullet$ Collected soil samples from experimental plots
\newline $\bullet$ Analyzed data and wrote research report}{}{}
\cventry{Nov.2008-Jan.2009}{Group member in a Popular Scientific Writing Project about Global Change}{Global Change -- Have you felt it?}{Wrote a chapter about five past mass extinctions and the situation of extinction nowadays in the book}{}{}
\cventry{Jul.2007}{Ecological Internship}{Yunnan Province (A global biodiversity hotspot), China}{
\newline $\bullet$ Been familiar with ecological research stations
\newline $\bullet$ Learned how to identify plant species}{}{}
\cventry{2006}{Leader of a four-people group in water quality monitoring of Dian Lake}{YNU}{}{}{}
\subsection{\textsc{Academia}}
\cventry{Jul.2010}{Low Carbon Development Symposium of Guangzhou}{Guangzhou, China}{}{}{}%helped organize the symposium
\cventry{Nov.2009}{\textbf{$23^{rd}$} New Phytologist Symposium: Carbon Cycling in Tropical Ecosystems}{Guangzhou, China}{Organized by New Phytologist Trust}{}{}
\cventry{Jul.2009}{National Summer School of Biodiversity for Postgraduates \& ACCENT(The European Network of Excellence in Atmospheric Composition Change) Workshop}{Guangzhou, China}{}{}{}
\subsection{\textsc{Teaching}}
\cventry{Sep.2010-}{Teaching Assistant for Restoration Ecology}{School of Life sciences, SYSU}{}{}{}

\section{\textsc{Publication}}
\subsection{\textsc{Peer-reviewed Publication}}
\cvline{}{Bosun Wang, Shaolin Peng, \textbf{Daijiang Li}, Ting Zhou. Research progress on \emph{Merremia boisiana}. Chinese Journal of Ecology, 2009, 28(11):2360-2365.\emph{(In Chinese with an English abstract)}}
%\subsection{\textsc{Books and Book chapters}}
\subsection{\textsc{Manuscripts in Preparation}}
\cvline{}{\textbf{Daijiang Li}, Shaolin Peng. Increased dominance of climbing plants influences litter decomposition process. \emph{in prep}.}

\section{\textsc{Research Interests}}
\cvline{}{Biodiversity and Ecosystem Functioning, Community Dynamics, Species Abundance, Species Invasion, Global Change Biology, Statistical Learning}

\section{\textsc{Computer Skills}}
\cvline{}{R, SPSS, Meta-Win, \LaTeX, JabRef, EndNote, Microsoft Office}
\end{document}

\section{\textsc{Updated}}
\cvitem{}{Oct 8. 2010}

\section{\textsc{Standardized Tests}}
\cvitem{}{\textbf{GRE General Tests Scores}}
\cvitem{Test Date}{Jun 12, 2010}
\cvitem{Quantitative}{800/800 \hspace{1.5cm} Percentile Rank: 94\%}
\cvitem{Verbal}{610/800 \hspace{1.5cm} Percentile Rank: 88\%}
\cvitem{Analytical}{3.0/6.0 \hspace{1.65cm} Percentile Rank: 10\%} %Analytical
\cvitem{}{\textbf{iBT TOEFL Scores}}
\cvitem{Test Date}{Sep 12, 2010}
\cvitem{Reading}{29/30}
\cvitem{Listening}{30/30}
\cvitem{Speaking}{20/30}
\cvitem{Writting}{27/30}
\cvitem{Total}{106/120}

\subsection{\textsc{Chapters in Books}}
\cvline{}{\textbf{Liyin Liang}.Part 2 in Chapter 1. The relationship between Carbon Dioxide and Greenhouse effect.In book:Global Change-Could you feel it? Shaolin Peng, Ting Zhou. 2009. China Meteorogical Press:Beijing,13-21.\emph{in chinese}.}
\cvline{}{\textbf{Liyin Liang}.Part 4 in Chapter 1. Who made the Gaia's coat get stained. In book:Global Change-Could you feel it? Shaolin Peng, Ting Zhou. 2009. China Meteorogical Press,Beijing,31-41.\emph{in chinese}.}
\cvline{}{\textbf{Liyin Liang}.Case Study in Chapter 2. RESILIENCE thinking:Sustaining Ecosystems and People in a Changing World. Written by Brian Walker and David Salt. Translated by Shaolin Peng \emph{et al}. 2010. Higher Education Press,Beijing,39-52.\emph{in chinese}.}


